A Hybrid Approach for News Recommender System using Optimization Methods

### 2021-03-12 paper/paper.tex
finished paper

\author{
    {\includegraphics[scale=0.07]{./images/spbu.png}\hspace{1mm}Alexander Smirnov}\\
	Department of Information and Analytical Systems\\
	Saint Petersburg State University\\
	Russia, Saint Petersburg\\
	\texttt{ru.alexander.smirnov@gmail.com} \\
	\And
	{\includegraphics[scale=0.07]{images/spbu.png}\hspace{1mm}Elena Mikhailova} \\
	Department of Information and Analytical Systems\\
	Saint Petersburg State University\\
	Russia, Saint Petersburg\\
	\texttt{e.mikhaylova@spbu.ru} \\
	%% \AND
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
}

@@

        \begin{itemize}
            \item \Cref{sec:related} describes the relevant related work
            \item \Cref{sec:input} describes input data
            \item \Cref{sec:overview} explains our modular design and architecture
            % \item \Cref{sec:implementation} describes the implementation of the algorithms in a real system
            \item \Cref{sec:evaluation} provides tests and experiments validating
our system’s results
            \item \Cref{sec:further} explains future work
            \item \Cref{sec:summary} presents conclusions
        \end{itemize}

@@

@@

\newpage
\section{Overview of our approach}
\label{sec:overview}

@@

$$r_i = \frac{(v_i - 1)}{(t - t_i + 2)^G}$$

@@

The score decreases as $t - t_i$ increases, meaning that older items will get lower and lower scores. $v_i$ gets substracted by $-1$ to negate submitter's view. $t - t_i$ increased by $2$ so even if $t - t_i = 0$ gravity factor $G$ will take effect.

@@

$r_{u i}=\sum_{f=0}^{n } H_{u, f} W_{f, i}$

@@

$r_{u i}=\mu+b_{i}+b_{u}+\sum_{f=0}^{n} H_{u, f} W_{f, i}$

@@

@@

\begin{itemize}
    \item \textbf{Topic 1:} ruble, bank, money, dollar
    \item \textbf{Topic 2:} cooking, sugar, gordon\_ramsay
    \item \textbf{Topic 3:} IT, smartphone, technology, hacker
\end{itemize}

And we have following text: ``Hackers use mobile emulators to steal millions of dollars''. Its vectorized form is going to be $[0.7, 0, 0.8]$.

@@

$$r_{i}=\sum_{k=0}^{n} \textit{similarity}\{\textit{current\_item\_vector}, \textit{last\_viewed\_vector}_{k}\} \times \textit{weight}_k$$

@@

    Also we have information about \hyperref[tab:show]{shows} and \hyperref[tab:view]{views}, so we are able to track what item in recommendation list was clicked and what item was skipped, so depending on this information we can track if user liked item or not.

@@

Results show that combining different approaches leads to rise of users' involvement.

>>>>

\author{
    {\includegraphics[scale=0.07]{./images/spbu.png}\hspace{1mm}Alexander Smirnov}\\
	Department of Information and Analytical Systems\\
	Saint Petersburg State University\\
	Russia, Saint Petersburg\\
	\texttt{ru.alexander.smirnov@gmail.com} \\
	\And
	{\includegraphics[scale=0.07]{images/spbu.png}\hspace{1mm}Elena Mikhailova} \\
	Department of Information and Analytical Systems\\
	Saint Petersburg State University\\
    ITMO university\\
	Russia, Saint Petersburg\\
	\texttt{e.mikhaylova@spbu.ru} \\
	%% \AND
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
}

@@

        \begin{itemize}
            \item \Cref{sec:related} describes the relevant related work
            \item \Cref{sec:overview} contains overview of our approch
            \item \Cref{sec:input} describes input data
            \item \Cref{sec:approach} explains our modular design and architecture
            % \item \Cref{sec:implementation} describes the implementation of the algorithms in a real system
            \item \Cref{sec:evaluation} provides tests and experiments validating
our system’s results
            \item \Cref{sec:summary} presents conclusions
        \end{itemize}

@@

\section{Overview of our approach}
\label{sec:overview}

@@

\newpage
\section{Our approach}
\label{sec:approach}

Lets describe in detail candidate generation ranking pipeline.

@@

\begin{equation}
    r_i = \frac{(v_i - 1)}{(t - t_i + 2)^G}
\end{equation}

@@

The score decreases as $t - t_i$ increases, meaning that older items will get lower and lower scores. $v_i$ gets substracted by $-1$ to negate submitter's view. $t - t_i$ increased by $2$ so even if $t - t_i = 0$ gravity factor $G$ will take effect. By default we set $G=1.8$ and we increase it if we want to prioritize newer news over old and vice versa.

@@

\begin{equation}
    r_{u i}=\sum_{f=0}^{n } H_{u, f} W_{f, i}
\end{equation}

@@

\begin{equation}
    r_{u i}=\mu+b_{i}+b_{u}+\sum_{f=0}^{n} H_{u, f} W_{f, i}
\end{equation}

@@

\begin{equation}
    r_i = \frac{\emph{shows\_num\_norm}}{4} + \frac{\emph{views\_num\_norm}}{4} + \frac{\emph{emotions\_num\_norm}}{4} + \frac{\emph{comments\_num\_norm}}{4} 
\end{equation}

@@

\begin{table}[h]
\centering
% \resizebox{\textwidth}{!}{%
\begin{tabular}{ccc}
    \toprule
\textit{topic} & \textit{word} & \textit{score} \\
    \midrule
1 & dollar & 0.3 \\
1 & bank & 0.2 \\
1 & money & 0.15 \\
2 & sugar & 0.4 \\
2 & cooking & 0.3 \\
3 & IT & 0.25 \\
3 & hacker & 0.2 \\
\bottomrule
\end{tabular}%
% }
\caption{words' topics}
\label{tab:words_topics}
\end{table}

And we have following text: ``Hackers use mobile emulators to steal millions of dollars''. Its vectorized form is going to be $[0.3, 0, 0.2]$.

@@

\begin{equation}
    r_{i}=\sum_{k=0}^{n} \textit{similarity}\{\textit{current\_item\_vector}, \textit{last\_viewed\_vector}_{k}\} \times \textit{weight}_k
\end{equation}

@@

    Also we have information about \hyperref[tab:show]{shows} and \hyperref[tab:view]{views}, so we are able to track what item in recommendation list was clicked and what item was skipped, so depending on this information we can track if user liked item or not. For instance, let's consider situation that user clicked on 4th recommendation from recommendation list. That means that first 3 recommedations are bad, and we should penalty recommenders that prioritized these items, considering the fact that 1st item is the worst:

\begin{equation}
    \textit{penalty} = \frac{1}{\textit{num\_of\_item\_in\_rank}}
\end{equation}

@@

Results show that combining different approaches leads to rise of users' involvement. Firstly we had only a collaborative recommender and user averagely spend on news tab around 2 minutes. Now when we applied hybrid recommender users spend in average 5 minutes on news tab.
